Interested in joining the team

### 2024-04-24 join.qmd
remove information about applying for 2024-25 academic year

**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now open.**

- Applications will be received until Friday, March 1, 2024
- Applicants selected for an interview will be notified by Friday, March 8, 2024
- Interviews will take place in mid-to-late March
- Offers for a practicum, project, or thesis position in the lab will be sent to selected students by Friday, March 29, 2024

>>>>

**The application period for practicum, project, and thesis courses for the 2024-25 academic year is now closed.**
